---
title: "Lab 00 - Hello IDS!"
author: "Marcel Drozdz the 8th"
date: "`r Sys.Date()`"
output: html_document
---

### Load packages and data

```{r load-packages, message=FALSE}
library(tidyverse) 
```

### Exercises 16-17

We set up the data frame. Edit the data below to include information about your team members.

```{r setup-tibble}
team_data <- tibble(
  name = c("Marcel William Drozdz the barbarian Equire MD the VIIIth", "SKY", "Siddhi", 
           "Hanna", "VIVI", "maggie"),
  github_username = c("Remotelamp", "lewotte", "SIDDHIsaxena27", 
                      "HannaHarull", "vivihuangx", "maggie034"), 
  colour = c("ROYAL BLUE", "cyan", "red", 
             "brown", "pink", "green"),
  hobby = c("Spinning", "weight lifting", "sleeping", 
            "tv", "drawing", "sleeping"),
  favourite_number = c(8, 5, 8, 75, 77, 1)
  )

team_data
```

### Exercise 18

We now work on visualising our data. 

```{r bar-plot}
p1 <- ggplot(data = team_data, 
             mapping = aes(x = github_username, 
                           y = favourite_number,
                           fill = colour), 
             ) +
   geom_col() +
   scale_fill_identity()
p1
```


It shows the data I entered

### Exercises 19

Change the text of the plot title and axis labels.

```{r labelled-bar-plot}
p1 + labs(x = "Username", 
          y = "Fav No.",
          title = "Fav No./Username")
```

*Remove this text (including the stars), and add your answer for Exercise 19 here.*

### Exercise 20

```{r new-bar-plot}
p2 <- ggplot(team_data, aes(x = hobby)) +
  geom_bar()
p2
```

*Remove this text (including the stars) and add your answer for Exercise 20 here.*
